pdp: An R Package for Creating Partial Dependence Plots

### 2016-09-19 manuscript/greenwell.tex
minor edits

Currently supported models are described in Table~\ref{tab:models}. However, the default method \code{partial.default} is flexible enough to handle many of the model types not listed in in this table; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} and projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package. Although, for these cases, the user will need to specify the additional options \code{type} (i.e., \code{"regression"} or \code{"classification"}) and \code{train} (the original training data) in the call to \code{partial}---the exception in Table~\ref{tab:models} is using partial with the \code{"xgb.Booster"} class, which requires the user to specify \code{train}.

@@

>>>>

Currently supported models are described in Table~\ref{tab:models}. In a lot of these cases, \code{partial} should be able to automatically determine \code{type} (i.e., \code{"regression"} or \code{"classification"}) and \code{train} (the original training data). In other cases, the user may need to specify these additional arguments. Using these additional arguments, it is possible to handle many of the model types not listed in in this table; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} and projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package.

@@

When additional arguments are necessary, the user will be prompted with an informative error message. For instance, the user may occasionally see the following:
\begin{example}
Error: The training data could not be extracted from object. Please supply the raw training data using the `train` argument in the call to `partial`.
\end{example}
This will occure, for example, when using partial with the \code{"xgb.Booster"} class. In fact, using \code{partial} with any object that does not store the original training data will result in the above error message.
